Neighborhoods and Felony Disenfranchisement: The Case of New York City

### 2019-06-03 markdown/kmorris_thesis.Rmd
more writing

Model 1 in Table \ref{tab:to-18-logit} formalizes the trend presented in Figure \ref{fig:to-18} by controlling only for whether an individual was discharged on or after May 21^st^, 2018, and the number of days between the individual's discharge date and November 6^th^, 2018. Model 2 also controls for individual-level characteristics: sex, age on November 6^th^, 2018, county, and race. Model 3 adds sentence-specific information to Model 2: the number of counts in the individual's most recent sentence, the amount of time they spent on parole, and the class of felony for which they were convicted. In each successive model, the AIC decreases substantially, indicating that including these controls are warranted. Table \ref{tab:to-18-logit} makes clear that formerly incarcerated men were far less likely to vote than formerly incarcerated women; that older formerly incarcerated individuals were more likely to cast a ballot; and individuals who spent longer on parole were more likely to participate in the midterm election.

>>>>

Model 1 in Table \ref{tab:to-18-logit} formalizes the trend presented in Figure \ref{fig:to-18} by controlling only for whether an individual was discharged on or after May 21^st^, 2018, and the number of days between the individual's discharge date and November 6^th^, 2018. Model 2 also controls for individual-level characteristics: sex, age on November 6^th^, 2018, county, and race. Model 3 adds sentence-specific information to Model 2: the number of counts in the individual's most recent sentence, the amount of time they spent on parole, and the class(es) of felony for which they were convicted. In each successive model, the AIC decreases substantially, indicating that including these controls are warranted. Table \ref{tab:to-18-logit} makes clear that formerly incarcerated men were far less likely to vote than formerly incarcerated women; that older formerly incarcerated individuals were more likely to cast a ballot; and individuals who spent longer on parole were more likely to participate in the midterm election.
